A Spiking Independent Accumulator Model for Winner-Take-All

### 2017-01-24 doc/paper/paper.tex
Be more explicit about range of indices.

\subsection{Leaky, competing accumulator model}
Using the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
The dynamics for each state variable $x_i(t),\ i < D$, where $D$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}):
\begin{equation} \label{eqn:usher-mcclelland}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} = \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau}, \quad x_i &\ge 0,
    \end{split}
\end{equation}
where $\rho_i$ is each external input, $k$ is the leak rate, $\beta$ the lateral inhibition, and $\tau$ the time-constant.
This model essentially integrates each input $\rho_i$ with a leak term ($- kx_i$), minus competition from every other variable ($\beta \sum_{j \neq i} x_j$).
Supposing $\rho_i > \rho_j$ for all $j \ne i$, a WTA mechanism should indicate that $i$ is the winning choice.
Setting $k = \beta = 1$ will guarantee that the winning state $x_i$ converges to the value of the largest input $\rho_i$, while the losing states $x_j$ ($j \ne i$) converge to zero.
Other choices of $k$ merely alter the effective $\tau$ and the effective gain on the input, while other choices of $\beta$ will produce unwanted behaviour (see supplementary analysis).

@@

The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ i < D$.
The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
From the second layer, we decode the function $\bar{x}_i := \Theta(x_i - \vartheta)$ where $\Theta$ is the Heaviside function, and $\vartheta = 0.8$ is a fixed threshold value that determines how much evidence needs to be accumulated to produce an output.
The Heaviside decoded output of layer 2 projects back to layer 1 to add $\bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j$ to the input of $x_i$.
Since intuitively the largest input will accumulate the fastest, once this reaches the threshold $\vartheta$ it will self-excite and inhibit all other state variables.
Fixing $\bar{\beta} = 2$ ensures that the losing state variables will go to zero (see supplementary analysis).
This is summarized more precisely by the following dynamics (see Fig.~\ref{fig:indacc}):
\begin{equation}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} = \rho_i \frac{1}{\tau_1} + \left( 
            \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2} , \quad x_i &\ge 0 .
    \end{split}
\end{equation}
Compared to the LCA model, the threshold $\vartheta$ is an additional free parameter that controls how quickly the IA model makes a decision and how much evidence will be integrated.
Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$ instead which is equivalent due to the leak-free integration.
% should we say anything about how the thresholding population works?

>>>>

\subsection{Leaky, competing accumulator model}
Using the NEF, we have implemented the widely-used leaky, competing accumulator (LCA) model proposed by~\citeA{usher2001}.
The dynamics for each state variable $x_i(t),\ 1 \leq i \leq D$, where $D$ is the number of choices, are given by~(see Fig.~\ref{fig:usher-mcclelland}):
\begin{equation} \label{eqn:usher-mcclelland}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} = \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau}, \quad x_i &\ge 0,
    \end{split}
\end{equation}
where $\rho_i$ is each external input, $k$ is the leak rate, $\beta$ the lateral inhibition, and $\tau$ the time-constant.
This model essentially integrates each input $\rho_i$ with a leak term ($- kx_i$), minus competition from every other variable ($\beta \sum_{j \neq i} x_j$).
Supposing $\rho_i > \rho_j$ for all $j \ne i$, a WTA mechanism should indicate that $i$ is the winning choice.
Setting $k = \beta = 1$ will guarantee that the winning state $x_i$ converges to the value of the largest input $\rho_i$, while the losing states $x_j$ ($j \ne i$) converge to zero.
Other choices of $k$ merely alter the effective $\tau$ and the effective gain on the input, while other choices of $\beta$ will produce unwanted behaviour (see supplementary analysis).

@@

The first layer consists of a separate integrator population (i.e., accumulator) for each state variable $x_i(t), \ 1 \leq i \leq D$.
The second layer consists of independent, non-recurrent populations that receive input from the first layer in a one-to-one fashion.
From the second layer, we decode the function $\bar{x}_i := \Theta(x_i - \vartheta)$ where $\Theta$ is the Heaviside function, and $\vartheta = 0.8$ is a fixed threshold value that determines how much evidence needs to be accumulated to produce an output.
The Heaviside decoded output of layer 2 projects back to layer 1 to add $\bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j$ to the input of $x_i$.
Since intuitively the largest input will accumulate the fastest, once this reaches the threshold $\vartheta$ it will self-excite and inhibit all other state variables.
Fixing $\bar{\beta} = 2$ ensures that the losing state variables will go to zero (see supplementary analysis).
This is summarized more precisely by the following dynamics (see Fig.~\ref{fig:indacc}):
\begin{equation}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} = \rho_i \frac{1}{\tau_1} + \left( 
            \bar{x}_i - \bar{\beta} \sum_{j \neq i} \bar{x}_j \right) \frac{1}{\tau_2} , \quad x_i &\ge 0 .
    \end{split}
\end{equation}
Compared to the LCA model, the threshold $\vartheta$ is an additional free parameter that controls how quickly the IA model makes a decision and how much evidence will be integrated.
Instead of directly manipulating $\vartheta$, we opt to change $\tau_1$ instead which is equivalent due to the leak-free integration.
% should we say anything about how the thresholding population works?
